### 2020-03-02 Common/structure/info.tex
Julien and Johan: title draft + remake figure

\thesistitle{Prostate Cancer Classification:\\A Freeze/Unfreeze Transfer Learning Approach} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
\supervisor{Prof. Dr. Philippe Cudré-Mauroux} % Your supervisor's name, this is used in the title page, print it elsewhere with \supname
\cosupervisor{Co-supervisor Name} % If you have a co-supervisor, include it here. This is used in the title page, print it elsewhere with \supname
\degree{Master} % Your degree name, this is used in the title page and abstract, print it elsewhere with \degreename
\author{Author Name} % Your name, this is used in the title page and abstract, print it elsewhere with \authorname
\addresses{Bd de Pérolles 90} % Your address, this is not currently used anywhere in the template, print it elsewhere with \addressname

>>>>

\thesistitle{Prostate Cancer Classification:\\A Freeze/Unfreeze Transfer Learning Approach Using Multiple Body Parts} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
\supervisor{Prof. Dr. Philippe Cudré-Mauroux} % Your supervisor's name, this is used in the title page, print it elsewhere with \supname
\cosupervisor{Co-supervisor Name} % If you have a co-supervisor, include it here. This is used in the title page, print it elsewhere with \supname
\degree{Master} % Your degree name, this is used in the title page and abstract, print it elsewhere with \degreename
\author{Author Name} % Your name, this is used in the title page and abstract, print it elsewhere with \authorname
\addresses{Bd de Pérolles 90} % Your address, this is not currently used anywhere in the template, print it elsewhere with \addressname
